\Huge \bf Implementation of a quadrotor UAV

### 2012-07-13 latex/paper/paper.tex
algunas chiquititos +

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

@@

\begin{abstract}
%\boldmath
This paper describes the design and integration of a control system that allows the autonomous flight of a radio controlled commercial quadcopter. A mathematical model for the quadcopter is developed, its parameters determined from the characterization of the unit. An external intelligence is integrated to play the rol of the flight controller. Sensors are calibrated and added to the platform, then combined within a Extended Kalman Filter to obtain an estimation of the state variables. The control actions are obtained from a proportional-integral control system based on the LQR algorithm.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

\section{Introduction}
% no \IEEEPARstart
This paper describes the design and integration of a control system that allows the autonomous flight of a radio controlled commercial quadcopter. A mathematical model for the quadcopter is developed, its parameters determined from the characterization of the unit. An external intelligence is integrated to play the rol of the flight controller. Sensors are calibrated and added to the platform, then combined within a Extended Kalman Filter to obtain an estimation of the state variables. The control actions are obtained from a proportional-integral control system based on the LQR algorithm.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill January 11, 2007

@@

>>>>

% Meto paquetes a huevo
\usepackage{graphicx}

% *** GRAPHICS RELATED PACKAGES ***
%
%\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
%\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
%\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

@@

\begin{abstract}
%\boldmath
This paper describes the design and integration of a control system that allows the autonomous flight of a radio controlled commercial quadcopter. A mathematical model for the quadcopter is developed, its parameters determined from the characterization of the unit. An external intelligence is integrated to play the rol of the flight controller. An IMU is calibrated and added to the platform. Data from a 9 degrees of freedom IMU equiped with a barometer is combined with the information provided by a GPS within a Extended Kalman Filter to obtain a reliable estimation of the state variables. The control actions are obtained from a proportional-integral control system based on the LQR algorithm.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

\section{Introduction}
% no \IEEEPARstart

A quadrotor platform can be imagined performing countless tasks. Many applications are being developed based on such platforms, but how do they fly? The start point of developing an unmanned aerial vehicle (UAV) is that it in inherently unstable, staying still is not a simple task. The platform is based on a commercial quadcopter, the frame and the motor control system were preserved, but the IMU and intelligence were replaced by the flight controller that was developed. An ARM-Cortex-A8 processor running Linux performs the computations requiered to convert raw IMU data and combine it using an Extended Kalman Filter, overcoming the noise generated by the vibrations of the motors, and providing a reliable estimation of the state variables. Once the current state is known, the LQR algorithm is used to derive control actions required to bring the system to the desired setpoint.

This paper explains how to deal with an IMU, the mathematical model behind the system, the filtering techniques requiered to achieve a reliable state estimation based on noisy data, and the control system that will allow putting a quadrotor into flight.

% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
%I wish you the best of success.

%\hfill mds

%\hfill January 11, 2007

@@

The equations that govern the dynamics of a quadcopter are bla.

\begin{equation}
\boxed{\begin{aligned}&\dot{x}=v_{q_x} \cos \varphi \cos \theta + v_{q_y} ( \cos \theta \sin \varphi \sin \psi-\cos \varphi \sin \theta )\\
&\quad + v_{q_z}(\sin \psi \sin \theta + \cos \psi \cos \theta \sin \varphi)\\
&\dot{y}=v_{q_x} \cos \varphi \sin \theta + v_{q_y} (\cos \psi \cos \theta + \sin \theta \sin \varphi \sin \psi)\\
&\quad+ v_{q_z}( \cos \psi \sin \theta \sin \varphi-\cos \theta \sin \psi )\\
&\dot{z}= -v_{q_x} \sin \varphi  + v_{q_y} \cos \varphi \sin \psi  + v_{q_z}\cos \varphi \cos \psi\\
&\dot{\psi}=\omega_{q_x} + \omega_{q_z}\tan\varphi \cos\psi + \omega_{q_y}\tan\varphi \sin\psi\\
&\dot{\varphi}=\omega_{q_y}\cos \psi - \omega_{q_z}\sin\psi\\
&\dot{\theta}=\omega_{q_z} \frac{\cos\psi}{\cos\varphi}  + \omega_{q_y}\frac{\sin\psi}{\cos\varphi}\\
&\dot{v_{q_x}}=v_{q_y} \omega_{q_z} - v_{q_z} \omega_{q_y}+g\sin\varphi\\
&\dot{v_{q_y}}=v_{q_z} \omega_{q_x} - v_{q_x} \omega_{q_z}-g\cos\varphi\sin\psi\\
&\dot{v_{q_z}}=v_{q_x} \omega_{q_y} - v_{q_y} \omega_{q_x}-g\cos\varphi\cos\psi+\frac{1}{M}\sum_{i=1}^4T_i\\
&\dot{\omega_{q_x}}=\frac{1}{I_{xx}}\omega_{q_y}\omega_{q_z}(I_{yy}-I_{zz})+\frac{1}{I_{xx}}\omega_{q_y}I_{zz_m}(\omega_1-\omega_2+\omega_3-\omega_4)\\
&\quad-\frac{1}{I_{xx}}dMg\cos\varphi\sin\psi+\frac{1}{I_{xx}}L(T_2-T_4)\\
&\dot{\omega_{q_y}}=\frac{\omega_{q_x}\omega_{q_z}(-I_{xx}+I_{zz})}{I_{yy}}+\frac{\omega_{q_x}I_{zz_m}(\omega_1-\omega_2+\omega_3-\omega_4)}{I_{yy}}\\
&\quad-\frac{dMg\sin\varphi}{{I_{yy}}}+\frac{L(T_3-T_1)}{I_{yy}}\\
&\dot{\omega_{q_z}}=\frac{-Q_1+Q_2-Q_3+Q_4}{I_{zz}}\\
%\frac{-I_{zz_m}(\dot{w_1}-\dot{w_2}+\dot{w_3}-\dot{w_4})}{I_{zz}}+
\end{aligned}}
\label{eq:modelo}
\end{equation}

\begin{figure}
	\centering
	\includegraphics[width=1\columnwidth]{./pics_paper/quad_coord.jpg}
	\caption{Model of a quadcopter}
	\label{fig:quad}
\end{figure}
